Dynamic Transition Analysis with TIMES

### 2019-01-04 doc/2019-01-poster/poster.tex
Updated plots, added poster tex
Former-commit-id: c311aeaf9285b06e2c774b9c3efc9d3be5f5f1b8 [formerly ac2aa4f57b7d4fe8bc67b991fd2642e96e46603e]
Former-commit-id: f39c455b1448ad396a78d3086f3f07df25093988

\begin{block}{Introduction}
Previous work has compared the impact of innovative energy technologies in 
various world regions using \textbf{static} scenario analyses 
\cite{chyong_chi_dynamics_2009,feng_system_2013,kikuchi_simulation-based_2017,li_energy_2010,pambudi_impact_2017,pambudi_future_2016}.  
We will simulate \textbf{dynamic} transition scenarios 
\cite{jebaraj_review_2006,pfenninger_energy_2014} aimed at minimizing carbon 
emissions in Japan by 2050. These scenarios will include realistic constraints 
regarding technology readiness (in terms of generation, transmission \& 
storage) and will combine multiple technologies in a single heterogeneous 
system model.
\end{block}

@@

%----------------------------------------------------------------------------------------
\begin{block}{Methodology}
        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
        \cite{loulou_documentation_2005} 
        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
        using linear and mixed-linear algorithms. A user-defined objective 
        function (such as minimizing carbon emissions or costs) is solved within user defined constraints such as energy generation demand.

\begin{description}
        \item[\textbf{Sector Analysis:}] TIMES models can resolve generation and 
                 consumption by sector (commercial, industrial, residential, 
                 building etc). 
         \item[\textbf{Regional Analysis:}] TIMES can also resolve regions.
         \item[\textbf{Post-Processing:}] Many metrics are automatically postprocessed 
                 (i.e. energy intensity, thermal energy efficiency, 
                 transmission capacity). 
         \item[\textbf{Constrained Optimization}] Modeling technology deployment 
                 transition as a constrained optimization problem will
                 drive insights.
 \end{description}

         The key objective function is minimization of carbon emissions in 2050 
         and a key
         constraint will be that deployed generation capacity must meet energy 
         demand. This can na\"ively be written:

\begin{align}
        \intertext{minimize:}
        &\sum_g^G C_g x_g 
        \intertext{subject to:}
        &\sum_g^Gx_g = d
        \intertext{where}
        C_g =& \mbox{ carbon emissions from generation component g}\\
        x_g =& \mbox{ deployment of generation component g}\\
        d =& \mbox{ generation demand}
\end{align}

A simple \textbf{static} formulation is straightforward to write, as above.  
However this  formulation is quickly complicated by including \textbf{dynamic 
time} as well as additional constraints (energy storage, variable demand, 
$CO_2$ sequestration, efficiency, costs, etc.)
\end{block}

\end{column} % End of column 2, top half
\end{columns}
%=======================================================
% Double Wide Figure Column 
%=========================================================
\input{model-fig}

@@

        \begin{alertblock}{Take Aways}
	\begin{itemize}
                \item Dynamic simulation of Japan's energy system transition in 
                        the TIMES model generator will help develop near-term 
                        decarbonization strategies.
                \item Policymakers will benefit from identification of high 
                        impact technologies, and creation of R\&D investment 
                        and infrastructure development timelines.  
                \item Simulations will quantify system sensitivity to 
                        technology readiness. 
                \item Dynamic analysis will identify potential transition 
                        bottlenecks.
	\end{itemize}
        \end{alertblock}

%--------------------------------------------------------
% PROJECT TIMELINE
%---------------------------------------------------------
\begin{block}{Timeline}
        \input{timeline}
\end{block}

>>>>

\begin{block}{Introduction}
Previous work has compared the impact of innovative energy technologies in 
various world regions using \textbf{static} scenario analyses 
\cite{chyong_chi_dynamics_2009,feng_system_2013,kikuchi_simulation-based_2017,li_energy_2010,pambudi_impact_2017,pambudi_future_2016}.  
We are simulating \textbf{dynamic} transition scenarios 
\cite{jebaraj_review_2006,pfenninger_energy_2014} aimed at optimizing energy supply to minimize carbon 
emissions in Japan to 80\% of 1990 levels by 2050, and maintaining these levels from 2050-2100. \\
Our simulation includes conventional energy sources such as \textbf{fossil fuels, nuclear energy, wind, solar, hydropower, and geothermal}, and applicable I$^2$CNER technologies like \textbf{post-combustion absorption-type carbon capture and sequestration, hydrogen production (steam reforming and photocatalytic conversion)}.
\end{block}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{conv_nuc_elc}
\caption{\textbf{Scenario 1} (conventional, with new nuclear) Electricity Generation.}
\label{s1e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{conv_nuc_co2}
\caption{\textbf{Scenario 1} (conventional, with new nuclear) CO$_2$ emissions.}
\label{s1c}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{conv_nonuc_elc}
\caption{\textbf{Scenario 2} (conventional, no new nuclear) Electricity Generation.}
\label{s2e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{conv_nonuc_co2}
\caption{\textbf{Scenario 2} (conventional, no new nuclear) CO$_2$ emissions.}
\label{s2c}
\end{figure}

@@

%----------------------------------------------------------------------------------------
\begin{block}{Methodology}
        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
        \cite{loulou_documentation_2005} 
        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
        using linear and mixed-linear algorithms. A user-defined objective 
        function is solved within user defined constraints.\hfill \break

\textbf{Key assumptions:}

\begin{itemize}
        \item\textbf{Objective function:} System cost.

         \item\textbf{Constraints:} CO$_2$ emissions, demand (+1.7\% per year).

         \item Hydropower capacity held constant

         \item All new nuclear power is based on ABWR designs.

         \item Growth rate and discrete investment size of nuclear, wind and solar is based on data and trends seen in the US, Chinese, and Japanese energy sectors.

         \item \textbf{Carbon capture and sequestration and steam reforming:} Deployed in 2030, with their costs reducing by 2050 as per projected trends.

         \item \textbf{Photocatalytic conversion:} Deployed in 2050, assumed to be cost-competitive with other H$_2$ producing technologies. \hfill \break

 \end{itemize}

We have modeled \textbf{four scenarios:}

\begin{description}
        \item[\textbf{Scenario 1:}]
        I$^2$CNER technologies \textbf{disabled}. Deployment of all conventional technologies, \textbf{including new ABWR reactors}, enabled (Fig. \ref{s1e} and \ref{s1c}.

        \item[\textbf{Scenario 2:}]
        I$^2$CNER technologies \textbf{disabled}. Deployment of all conventional technologies, \textbf{except new ABWR reactors}, enabled (Fig. \ref{s2e} and \ref{s2c}).

        \item[\textbf{Scenario 3:}]
        I$^2$CNER technologies \textbf{enabled}.  Deployment of all conventional technologies, \textbf{including new ABWR reactors}, enabled. (Fig.\ref{s3e} and \ref{s3c}).

        \item[\textbf{Scenario 4:}] 
 I$^2$CNER technologies \textbf{enabled}. Deployment of all conventional technologies, \textbf{excluding new ABWR reactors}, enabled (Fig.\ref{s4e} and \ref{s4c})

\end{description}

\vspace{11mm}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{i2cner_nuc_elc}
\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) Electricity Generation.}
\label{s3e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{i2cner_nuc_co2}
\caption{\textbf{Scenario 3} (with I$^2$CNER tech and new nuclear) CO$_2$ emissions.}
\label{s3c}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{i2cner_nonuc_elc}
\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) Electricity Generation.}
\label{s4e}
\end{figure}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{i2cner_nonuc_co2}
\caption{\textbf{Scenario 4} (with I$^2$CNER tech, no new nuclear) CO$_2$ emissions.}
\label{s4c}
\end{figure}

\end{column} % End of column 2, top half
\end{columns}
%=======================================================
% Double Wide Figure Column 
%=========================================================
%\input{model-fig}

@@

         \begin{alertblock}{Take Aways}
	\begin{itemize}
                \item Nuclear power has the lowest emissions intensity and it results in the most economical energy mix, despite high investment costs.

                \item Without nuclear and I$^2$CNER technology, solar and offshore wind must be deployed in a 1:2 ratio for grid resilience

                \item Cost competitive photocatalytic H$_2$ and offshore wind can replace nuclear, resulting in significantly higher system costs.

                \item Technologies with the highest impact: nuclear power, offshore wind, photocatalytic H$_2$ generation, solar power
	\end{itemize}
        \end{alertblock}

%--------------------------------------------------------
% PROJECT TIMELINE
%---------------------------------------------------------
\begin{block}{Future work}
    no
\end{block}
